\documentclass{amsart}

\usepackage{amsmath, amsfonts}
\author{jaeminoh}
\title{frank jones integration theory solutions}

\begin{document}
\maketitle

\section*{chapter 6}
\subsection*{section A}\hfill \\

Problem 1. "the vanishing property"\\

First, assume that $\int f d\mu = 0$. Since $f$ is measurable, there exists
an increasing seqeunce of nonnegative simple functions which converges to $f$. Let
denote them as $s_n$. Then $f^{-1}((0, \infty]) = \bigcup_{n=1}^{\infty}s_n ^{-1}((0, \infty])$, union of measure zero set.
Therefore, we get $\mu(f^{-1}((0, \infty])) = 0$.

Conversely, assume that $\int f d\mu > 0$. Then there exists nonnegative
simple function $s \leq f$ such that $\int s d\mu > 0$. Also we can write $s$ as
a linear combination of (measurable) characteristic functions, i.e. $\int s d \mu = \sum_{i=1}^N \alpha_i \mu(A_i) >0$.
So, $\alpha_i \mu(A_i) > 0$ for at least one integer $1 \leq i \leq N$. By Observing the fact that $A_i \subset f^{-1}((0, \infty])$,
we can conclude that $f^{-1}((0, \infty])$ has measure zero implies $\int f d \mu = 0$ by contrapositive.\\

Problem 2. "the finiteness property"\\

$E = \{x: f(x) = \infty \}$ is a measurable set since $f$ is measurable.
Suppose $\mu(E) > 0$. For any $M \in \mathbb{N}$, choose nonnegative simple measurable function $s_M \leq f$ such that $s_M(x) \geq M$ for $x \in E$.
Then $\int f d\mu \geq \int s_M d\mu \geq M \mu(E)$. Therefore, $\int f d\mu \geq M \mu(E)$ for all positive integer $M$.
It means that $\int f d\mu = \infty$. By taking contrapositive, we get what we want.\\

Problem 3. "compatibility to not finite nonnegative simple functions" \\

We are only interested in the case when $\alpha_k = \infty, \mu(A_k) > 0$.
Since $f$ is measurable, we can consider seqeunce of nonnegative finite simple function
$\{ t_n\}$ such that $t_n(x) \geq n$ for $x \in A_k$.
Therefore, $\int f d\mu \geq \int t_n d\mu \geq \mu(A_k)n$ for all positive integer $n$, which means $\int f d\mu = \infty$.
For other cases, it is easy to check the compatibility.\\

Problem 4. "scalar multiplication is still valid for $c = \infty$" \\

First, assume $\int f d\mu = 0$. Then $\mu(f^{-1}((0, \infty])) = 0$ by Problem 1.
It is obvious that $g^{-1}((0, \infty]) = f^{-1}((0, \infty])$ for $g = \infty f$.
So, $\int g d\mu = 0$. Therefore we get $\int \infty f d\mu = \int f d\mu$.

Second, assume $\int f d\mu > 0$. Then measure of $g ^ {-1} ((0, \infty ])$ is positive.
So, $\int \infty f d \mu = 0 \mu ( g ^ {-1} (0)) + \infty \mu(g^{-1}((0, \infty]))$ which is $\infty$.\\

Problem 5. "strict inequality for Fatou's lemma'\\

Consider this nonnegative finite simple function defined on real line:
\begin{equation*}
    s_n(x) = \begin{cases}
        n^2 & \text{if } x \in (0, {1 \over n}) \\
        0 & \text{otherwise}
    \end{cases}
\end{equation*}
$\lim s_n = 0$ and $\lim \int s_n d\mu = \infty$.\\

Problem 6.\\

Let $f_k = 1_{A_k}$ where $1_{A_k}$ is an indicator(characteristic) function.
By Fatou's lemma (ILLLI), $\int \liminf_{k \rightarrow \infty} 1_{A_k} d\mu \leq \liminf_{k \rightarrow \infty} \int 1_{A_k}d\mu = \liminf_{k \rightarrow \infty} \mu(A_k)$.
Now, showing $1_{\liminf A_k} \leq \liminf_{k\rightarrow \infty}1_{A_k}$ is left to us.
If $x \in \liminf A_k$ then $x \in \bigcap_{i\geq n} A_i$ for some positive integer $n$.
Then $1_{A_i}(x) = 1$ for all positive integer $i$ greater than $n$. So, $1_{\liminf A_k} \leq \inf_{i\geq n} 1_{A_i}$.
By letting $n \rightarrow \infty$, we get $1_{\liminf A_k} \leq \liminf_{k\rightarrow \infty}1_{A_k}$.
Therefore, $\mu(\liminf A_k) = \int 1_{\liminf A_k}d\mu \leq \int \liminf_{k \rightarrow \infty} 1_{A_k} d\mu \leq \liminf_{k \rightarrow \infty} \int 1_{A_k}d\mu = \liminf_{k \rightarrow \infty} \mu(A_k)$.\\

\subsection*{section B}\hfill \\

Problem 9. "iff condition for (finite) integrability"\\

Let $f\in \mathcal{L}^1(\mu)$. Then $\int f_{\pm} d\mu < \infty$, so there sum is also finite ( $= \int \lvert f \rvert d\mu$).

Conversely, assume $\lvert f \rvert \in \mathcal{L}^1(\mu)$. Then $\int f_{\pm} d\mu \leq \int \lvert f \rvert d\mu < \infty$. Therefore $f \in \mathcal{L}^1(\mu)$.\\

Problem 10. "dominated integrability"\\

If $f$ is measurable, $f_{\pm}$ is also measurable. So $f_+ + f_- = \lvert f \rvert $ is measurable.
$\int \lvert f \rvert d\mu \leq \int \lvert g \rvert d\mu < \infty$. 
Therefore, $\lvert f \rvert \in \mathcal{L}^1(\mu)$ by Problem 9.\\

Problem 11. \\

It is obvious that $ \lvert f_k \rvert \leq \lvert f \rvert$ and $f \in \mathcal{L}^1(\mu)$.
So, if each $f_k$s are measurable, by dominated convergence thm, done.
Actually, $f_k = f \cdot 1_{A_k \cap E_k}$ where $A_k = \left [ -k, k \right ]$ and $E_k = f^{-1} (\left [ -k, k \right])$.
There exists sequence of nonnegative finite simple function $\{s_i\}$ which converges to $f$ since $f$ is measurable.
So, $\lim s_i 1_{a_k \cap E_k} = f_k$ is measurable.\\

Problem 12. \\

Likewise, it is enough to show that $f(x) e^{-{ {\lvert x \rvert}^2 \over k}} = f_k(x)$ is measurable.
$e^{-{ {\lvert x \rvert}^2 \over k}}$ is continuous, hence Borel measurable, hence Lebesgue measurable.
There exists sequence of nonnegative finite simple function $\{s_k \}$ which converges to $f$ since $f$ is measurable.
So, $\lim_{i \rightarrow \infty} s_i e^{-{ {\lvert x \rvert}^2 \over k}} = f_k$ is measurable. \\

Problem 13. 'alternative proof for problem 2.42' \\

For each $x \in X$, there are at most $d\in \mathbb{N}$ distinct $A_k$ containing $x$.
Fix positive integer $N$. Let $I_x = \{ k \in \mathbb{N} : k \leq N \text{ and } x\in A_k\}$.
Clearly $\sum_{k=1}^N 1_{A_k} \leq d 1_A$ where $A = \bigcup_{i=1}^{\infty}A_i$.
By integrating both sides, $\sum_{k=1}^N \mu(A_k) \leq d \mu(A)$.
By Letting $N \rightarrow \infty$, we got the result in Problem 2.42.

(similar, another) $\sum_{k=1}^N 1_{A_k} \leq \left | I_x \right | \leq d = d 1_A$ for all N.
So $\sum_{k=1}^{\infty} 1_{A_k} \leq d1_A$.
By integrating both sides and monotone convergence thm, we got it.\\

Problem 14. \\

Let $\mathcal{I}$ be set of all sequences which are strictly increasing positive integers and length $m$.
Such set is countable. Now, $\bigcup_{i \in \mathcal{I}} \bigcap_{j=1}^m A_{i_j} = E_m$ and it is measurable.

Similar to Problem 13, $m 1_{E_m} \leq \sum_{i=1}^{\infty}1_{A_i}$.
So, $m \mu(E_m) = \int m 1_{E_m} d\mu \leq \int \sum_{i=1}^{\infty}1_{A_i} d\mu = \sum_{i=1}^{\infty} \int 1_{A_i} d\mu = \sum_{i=1}^{\infty}\mu(A_i)$ by monotone convergence thm.

\subsection*{section C} \hfill \\

Problem 16. \\

Clearly, $ \lvert f \rvert = 0$ almost everywhere, and $\lvert f \rvert$ is measurable.
Consider nonnegative finite simple function $s \leq \lvert f \rvert$. Then $s=0$ almost everywhere
and $s = \sum_{i=1}^N \alpha_i 1_{A_i}$, where $A_i$ is null set if $\alpha_i \ne 0$.
Therefore, $\int s d\mu = 0$, which implies $\int \lvert f \rvert d\mu = 0$.
So, $f \in \mathcal{L}^1(\mu)$, $\left | \int f d \mu \right | =0 \Rightarrow \int f d \mu = 0$.\\

Problem 17. \\

Note that $f \sim g \Leftrightarrow f = g\text{ a.e.}$ is an equivalence relation.
So, $g = h \text{ a.e}$.
Let g be measurable and $E_t = \left [ -\infty, t \right]$, $N = \{ x : g(x) \ne h(x)\}$.
Then $h^{-1}(E_t) \setminus g^{-1}(E_t) \subset N$ and $g^{-1}(E_t) \setminus h^{-1}(E_t) \subset N$.
Since $\mu$ is complete, they are all null sets. So $h^{-1}(E_t) \cup g^{-1}(E_t)$ is measurable.
Therefore, $h^{-1}(E_t)$ is also measurable, which implies measurability of $h$.\\


\end{document}